Ecological network control

### 2018-06-18 paper/supp-info.Rmd
Degree and response plot for species level models

# Empirical vs. random expectation of controllability {#randomisations}

>>>>

```{r fig-species-models-degree, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between degree and (a) the control capacity and (b) the probability of being a superior node. The plots show the values predicted by most parsimonious model for each response variable. The invasive species are depicted with solid orange circles."}
drake::loadd(fig_models_degree)
library(ggplot2)
fig_models_degree %<>% add_internal_margins()
cowplot::plot_grid(plotlist = fig_models_degree, ncol = 2)
```
